### 2018-06-18 paper/1-intro.tex
Work on S5

\item Moreover, we can readily remix the ingredients to describe the first
  build system that supports both \emph{dynamic dependencies}
  and \emph{cloud build} (\S\ref{sec-implementation-cloud-shake}).

>>>>

\item Moreover, we can readily remix the ingredients to describe the first
  build system that supports both \emph{dynamic dependencies}
  and \emph{cloud build} (\S\ref{sec-implementation-bazel-cloud-shake}).

### 2018-06-18 paper/2-background.tex
Work on S5

In this paper we elucidate which build system properties are consequences of
specific implementation choices (metadata and algorithm), and how one can obtain
new build systems with desired properties by recombining parts of existing
implementations. As a compelling example, we demonstrate how to combine the
advantages of \Shake and \Bazel in a cloud build system with dynamic
dependencies, see~\S\ref{sec-implementation-cloud-shake}.

>>>>

In this paper we elucidate which build system properties are consequences of
specific implementation choices (metadata and algorithm), and how one can obtain
new build systems with desired properties by recombining parts of existing
implementations. As a compelling example, we demonstrate how to combine the
advantages of \Shake and \Bazel in a cloud build system with dynamic
dependencies, see~\S\ref{sec-implementation-bazel-cloud-shake}.

### 2018-06-18 paper/4-build.tex
Work on S5

With the information in this section we can build a table comparing the
dependency order strategy with the out-of-date keys strategy, providing 9~possible
build systems, 5~of which are actually inhabited by existing build systems
(we discuss \Ninja \cite{ninja} in \S\ref{sec-related-build}). Of the
remaining 4~spots, we believe neither Traced or Cloud \Excel make sense~--~the
\Excel approach of reordering combined with static approximations reduces
the memory usage significantly. However, as soon as you are paying the cost of
storing traces, that benefit is gone. The advantage of Approximate \Shake over
\Shake would be that it could avoid storing traces and having a separate
information database, but that advantage is minor compared to the technical
restrictions and approximations it would provide, so we consider it unlikely
to be built. The Cloud \Shake system is an interesting and important point in
the design space, which we explore further in~\S\ref{sec-implementation-cloud-shake}.

>>>>

With the information in this section we can build a table comparing the
dependency order strategy with the out-of-date keys strategy, providing 9~possible
build systems, 5~of which are actually inhabited by existing build systems
(we discuss \Ninja \cite{ninja} in \S\ref{sec-related-build}). Of the
remaining 4~spots, we believe neither Traced or Cloud \Excel make sense~--~the
\Excel approach of reordering combined with static approximations reduces
the memory usage significantly. However, as soon as you are paying the cost of
storing traces, that benefit is gone. The advantage of Approximate \Shake over
\Shake would be that it could avoid storing traces and having a separate
information database, but that advantage is minor compared to the technical
restrictions and approximations it would provide, so we consider it unlikely
to be built. The Cloud \Shake system is an interesting and important point in
the design space, which we explore further
in~\S\ref{sec-implementation-bazel-cloud-shake}.
